Title

### 2019-05-03 paper_notes.Rmd
check history

@zhang2004residential cites and refers to @schelling1978micromotives for his prominent influence on threshold and tipping model, still then elaborates on a model based on random utility with single-peaked function and $\beta$. How much can a rational model which uses peak of utility and probability of choice be considered to rely on Schelling's threshold model?\
What is the relation between random utility models and threshold models?

>>>>

@zhang2004residential cites and refers to @schelling1978micromotives for his prominent influence on threshold and tipping model, still then elaborates on a model based on random utility with single-peaked function and $\beta$. How much can a rational model which uses peak of utility and probability of choice be considered to rely on Schelling's threshold model?
What is the relation between random utility models and threshold models?
